Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
modified FIG2

\begin{figure}[!t]
\centering
\includegraphics{FIG2_15-TIE-3480.pdf}
\caption{A set of $2$ periodic tasks scheduled under RMS algorithm and
  the implementation, respectively. $T=T_1=10$, $T_2=20$, $C_1=3$,
  $C_2=2$. In~(b), we assume both scheduling time and switching time
  are $2$.}
\label{f:example}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
\includegraphics{FIG2_15-TIE-3480.pdf}
\caption{A set of $2$ periodic tasks scheduled under (a) RMS algorithm
  and (b) the RMS implementation, respectively. $T=T_1=10$, $T_2=20$,
  $C_1=3$, $C_2=2$. In~(b), both scheduling time and switching time
  are $2$.}
\label{f:example}
\end{figure}
